Optimal (Multiway) Spatial Joins

### 2024-05-30 msj.tex
yufei

\extraspacing {\bf Algorithm for Problem $\bm{\mathscr{A}}$.} The {\em interval tree} \cite{bcko08} stores a set $S$ of $N$ intervals in $\real$ using $O(N)$ space such that, given any real value $q$, the intervals of $S$ containing $q$ can be found in $O(\log N + K)$ time, where $K$ is the number of intervals reported. It can also be used to detect whether $S$ has at least one interval containing $q$ in $O(\log N)$ time. Each interval insertion or deletion on $S$ can be supported in $O(\log N)$ time.

@@

\extraspacing {\bf Algorithm for Problem $\bm{\mathscr{C}}$.} Let $S$ be a set of $N$ intervals in $\real$, each of which is associated with a real-valued {\em weight}. Given a search value $q$, a {\em stabbing max} query returns the maximum weight of all the intervals in $S$ covering $q$ (if no such intervals exist, the query returns $-\infty$). We can store $S$ in a structure of \cite{aak+12} using $O(N)$ space that can answer every query in $O(\log N)$ time. The structure also supports an insertion or deletion on $S$ in $O(\log N)$ amortized time.

@@

%\input{4.3.tex}

>>>>

\extraspacing {\bf Algorithm for Problem $\bm{\mathscr{A}}$.} The {\em interval tree} \cite{bcko08} stores a set $S$ of intervals in $\real$ using $O(|S|)$ space such that, given any real value $q$, the intervals of $S$ containing $q$ can be found in $O(\log |S| + K)$ time, where $K$ is the number of intervals reported. It can also be used to detect whether $S$ has at least one interval containing $q$ in $O(\log |S|)$ time. Each interval insertion or deletion on $S$ can be supported in $O(\log |S|)$ time.

@@

\extraspacing {\bf Algorithm for Problem $\bm{\mathscr{C}}$.} Let $S$ be a set of intervals in $\real$, each of which is associated with a real-valued {\em weight}. Given a real value $q$, a {\em stabbing max} query returns the maximum weight of all the intervals in $S$ covering $q$ (if no such intervals exist, the query returns $-\infty$). We can store $S$ in a structure of \cite{aak+12} using $O(|S|)$ space that can answer every query in $O(\log |S|)$ time. The structure also supports an insertion or deletion on $S$ in $O(\log |S|)$ amortized time.

@@

\input{4.3.tex}
